---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alyssa Hawker"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The file has 1846 rows and 3 columns. The variables included in the data frame are dataset, x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
ANSWER: The correlation between `x` and `y` in this dataset is r = -0.06447185	


### Exercise 3

Plotting the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Next calculate the correlation between `x` and `y` in this star dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

ANSWER: The correlation between `x` and `y` in this star dataset is r = -0.0629611 which is very similar to the dino dataset (r = -0.06447185).	

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)