---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alyssa Hawker"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 7
    highlight: haddock
    theme: yeti
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The file has 1846 rows and 3 columns. The variables included in the data frame are dataset, x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
ANSWER: The correlation between `x` and `y` in this dataset is r = -0.06447185 which is a very weak negative correlation.


### Exercise 3

Plotting the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Next calculate the correlation between `x` and `y` in this star dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

ANSWER: The correlation between `x` and `y` in this star dataset is r = -0.0629611 which is also a very weak negative correlation and similar to the dino dataset (r = -0.06447185).	

### Exercise 4

Plotting the data in the circle dataset

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Next calculate the correlation between `x` and `y` in this circle dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

ANSWER: The correlation between `x` and `y` in this circle dataset is r = -0.06834336	which is very weak and also similar to the dino dataset (r = -0.06447185).	

### Exercise 5

Plotting the data in the entire datasaurus_dozen dataset:

```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Calculating the correlation between `x` and `y` for each group in the entire datasaurus_dozen dataset:

```{r corr-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```


All of the groups in the datasaurus dataset have correlations of r ~ -0.06. These are all very weak negative correlations that could basically be considered to be no correlation at all. This makes sense because the plots are all just fun images and not a relationship between two variables where a trend can be analyzed.


